\textit{*This acknowledgment contains plenty of subtexts and would be found as text within brackets. The subtext is meant to serve the purpose of comic relief and comic relief only.} \\

This thesis is no way an individual work. It is a product of a lot of love and sacrifice, tears and sweat of not just me but for various individuals who have taught lessons throughout my journey as a graduate student, here at NCSU. Although, I have endeavored to acknowledge everyone who has touched my life [for better or for worse], this list is in no way comprehensive. 

One of the primary reasons, I can write this thesis is because of Dr. George N. Rouskas and my aunt, Dr. Latha Unni. 
My first year at NCSU was tumultuous and eventful. As new graduate student, dealing with the stresses of graduate school and the unfavorable environment of my previous lab was overwhelming. This resulted in me [prematurely] deciding to quit graduate school---which I have been so excited to attend. Dr. Rouskas, who provided me with financial support while transitioning from my old advisor to my current advisor. Dr. Rouskas and my aunt counseled and provided support when I needed it the most. This thesis would have never been possible without these two amazing people. 

Secondly my thesis advisor [my academic father], Dr. Menzies, he is a legend [faking the
Aussie accent]. He has been very [not so] patient with me and directed me towards areas which
held promise. He helped me understand the value of collaboration and being a voracious reader
of the literature. That said I have never had a more dramatic relationship with anyone, which
in retrospect is an effective way of training graduate student. Our story has all the elements
of a soap opera, there are love and respect, not so much love [hate sounds just too strong] and
doubt. Either way, he played a massive part in making this thesis possible and made me a better
researcher [hopefully]. Also, he is also a reason I went to a trip around Europe [with Dr. Fu and George].

Thirdly, I would then like to thank my dissertation committee members,
Dr. Ranga Raju Vatsavai, Dr. Min Chi and Dr. Kathryn T. Stolee,
for their valuable feedback and insight on my dissertation.

I am also grateful to my research collaborators: Sven Apel (University of Passau), Norbert Siegmund (Bauhaus-University Weimar), and Pooyan Jamshidi (University of South Carolina), Jianfeng Chen (North Carolina State University).  I would like to gratefully acknowledge researchers who generously shared their research tools and results used in my dissertation.  I am very much
thankful to all my peers at the RAISE Lab, for their constant support, and useful feedback on
my research. I thank Dr. Wei Fu, Dr. Chin-Jung Hsu, Rahul Krishna, George Mathew, and Zhe Yu for the insightful and exciting conversations [interestingly I was able to write papers with all these amazing individuals---so all our discussions were not completely useless---as noted by Dr. Fu in his thesis acknowledgement]. 
I thank my internship mentors in the industry, who have immensely helped me expand
my research to a broader scope: Dan Camper and Arjuna Chala (LexisNexis Risk Solutions), and Chris Duvarney, Kim Herzig, and Hitesh Sajnani (Microsoft Research, USA). 


I extend heartfelt thanks to Kathy Luca, Carol Allen, and all the helpful staff at the Department
of Computer Science. I thank Amruthkiran Hedge, Anand Gorthi, Sandesh Saokar, Siddartha Chauhan, Mayank Vaish, Akhilesh Tanneru [Mr. T], and George Mathew for
sharing the apartment and making my stay at Raleigh eventful. Special thanks to Karen Warmbein, Blue and [Z]Simba whose love and support helped me survive the grind.



Finally, last but not least, I am very thankful to my family and friends. My family and friends were my constant source of support and encouragement throughout my journey as a doctoral student. 
My Ph.D. journey would not have gone so far, without y\textquotesingle all.