\section{Open Performance Data}
\label{sec:cat::dataset}

To evaluate a \cat method,
we need large-scale performance dataset---evaluating diverse workloads on different architectural choices.
We conducted a large-scale evaluation using different workloads and software systems on Amazon Web Services (AWS)~\cite{aws}.
We choose Apache Hadoop (version 2.7) and Apache Spark (version 1.5 and 2.1) as our software system~\cite{hadoop, spark}.
Our evaluation includes data processing, OLAP queries, and machine learning, which are popular applications on Hadoop and Spark.
We choose 18 VMs and run the 30 applications on them. \mytable{\ref{tab:dataset}} lists all the software systems and
applications.



\input{Chapter-CAT/tables/dataset}


We also vary the input size or input parameters to the applications for creating diverse workloads~\cite{Dalibard2017}.
When workloads are different, the optimal VM type (even for the same application) might change as well.
%Consequently, the optimal VM type for a given workload with different inputs might also change.
% Throughout this paper, we use workloads to represent applications with different inputs.
By running workloads with different data sizes, we can observe whether a particular VM can sustain increasing resource requirements (of a workload).
Our motivation (for the large-scale study) was to diversify the workloads such that we can extensively benchmark VMs.
In this study, each workload is tested with three different inputs sizes.
Some tests failed because smaller VM instances run out of memory.
Those are excluded in our data set.
In total, we measure the performance and collect the low-level information of 107 workloads on 18 different VM types.
We also collect 18 workloads on 69 multi-node configurations.
\mytable{\ref{tab:dataset_overview}} summarizes the dataset collection.

\input{Chapter-CAT/tables/dataset_overview.tex}


Performance optimization requires continuous efforts
to keep up with the rapid pace of cloud computing.
In our experience, performance data is hard to find.
A lack of performance data discourages the advances
in system performance research.
We believe that we will see advances in performance optimization
by sharing performance data.
Our large-scale performance dataset is available at
\url{https://github.com/oxhead/scout}.
